Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Remove irrelevant Appendix

%% ------------------------------------------------------------------------------------ %% 
\section{B. Extraction of 1-D surface brightness profile} 
    \label{app:ellipse}

@@

    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
    objects around the target.
    At the depth of the HSC images, this becomes a quite difficult task, especially 
    for massive galaxies with extended outer profiles and more satellites. 
    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
    we therefore perform \texttt{SExtractor}-like background subtraction and object 
    detection using the \texttt{SEP} Python library to generate the necessary masks.
    Combining two different local background models and $S/N$ thresholds, we obtain 
    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
    the one that is close to the center of bright galaxy (left panel of 
    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
    information. 
    We first create the mask that covers all contaminating objects around the target 
    after adaptively increasing the sizes of their masks according to their brightness 
    and distance to the target center. 
    Generally speaking, we mask out the very bright objects or objects in the 
    outskirt of the target a little more aggressively as they could impact the 
    low surface brightness regions more significantly. 
    We also create masks that are less and more aggressive to test their impacts
    on the surface brightness profiles.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
    \label{app:sed}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The format is very similar to the left panel of Fig~\ref{fig:mass_complete}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.~~
        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
        \nbcg{} (grey-black) galaxies using the samples matched on the 
        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
    \label{fig:gama}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
    (\citealt{Liske2015}) and see the impact of deep photometry again.

    We summarize the results in Fig~\ref{fig:gama}.  
    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
    consistent with the expectation from deeper photometry, although the 
    systematic differences in the estimates of \m2l{} could play a role here. 
    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
    becomes increasingly larger than \mtot{}, and most of these massive 
    galaxies have very high \ser{} index from the 2-D fitting. 
    This suggests that the single-\ser{} model is no longer an appropriate one to 
    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
    inner and/or outer regions.

    To verify the cause of the difference in \mstar{}, we further select samples 
    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
    and compare their \mden{} profiles (right panel). 
    Although these two subsamples are equally massive according to results from 
    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
    outer envelope, even though its median \mden{} profile is very similar 
    to the \nbcg{} sample at $< 10$ kpc. 
    We can reproduce very the same trend with the luminosity density profiles 
    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
    model definitely leads to under-estimate of \mstar{}.

\section{E. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering 
    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
    \caption{
        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
        We show the individual profile in the background using much thinner line, 
        and highlight the median profiles using thicker line and darker color.
        Other formats are exactly the same with the left figure of 
        Fig~\ref{fig:avg_prof}.}
    \label{fig:avg_prof_z}
\end{figure}    
%% ------------------------------------------------------------------------------------ %%

    Given the redshift range for our samples, it is important to evaluate 
    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
    profiles at different redshift. 
    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
    vulnerable to the PSF smearing effect at the center. 
    It is also harder to reach to the same \mden{} level under the same imaging depth 
    due to cosmological dimming and background noise.

    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
    and compare their \mden{} profiles. 
    In two redshift bins, the median \mden{} profiles from the same sample follow each 
    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
    where the effect from seeing kicks in. 
    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
    are identical in the central region, which indicates similar average seeing 
    conditions.       
    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
    and difference in redshift.
    More importantly, it also suggests that, once the redshift distributions are 
    carefully matched, the difference of \mden{} profile is likely to be physical 
    even in the central region.

\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering 
    \includegraphics[width=\textwidth]{fig/redbcg_match}
    \caption{
        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
        corresponding to the results shown in the left figure of   
        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
        whose size reflects the $P_{\mathrm{Cen}}$ value.  
        We also color-code them using the richness ($\lambda$) of the host cluster. 
        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
        To further evaluate the matching results, we show the distributions of \mtot{} 
        (middle panel) and redshift (bottom panel) separately. 
        On both panesl, we show the histograms along with their kernel density 
        distributions.  
        And, on the top of each panel, two sets of short vertical lines highlight the median 
        value (solid) and the inter-quartile (dash) of each distribution.~~~
        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
        samples used for the right figure of Fig~\ref{fig:prof_1}.
        The format is exactly the same as the left one, except the \minn{} replaces the 
        \mtot{} in the top and middle panels.}
    \label{fig:match}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

    As explained earlier, it is important to make sure the two samples have similar 
    distributions in both \mstar{} and redshift before comparing their median \mden{} 
    profiles.  
    Here we briefly describe the procedure used in this work. 
    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
    distributions of both parameters (as shown in Fig~\ref{fig:match}).

    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
    adjust the value of $N$ to achieve the best match. 
    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
    to split the sample into two redshift bins and match them separately. 
    Typically $N$ is between 3 to 8.
    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
    (Right), and the two samples are well matched in the distributions of \mtot{}
    (or \minn{}) and redshift.  
    For all the comparisons of \mden{} profiles in this work, we match the samples 
    in the same way, and make sure the match has the same quality.

%% ------------------------------------------------------------------------------------ %% 
\section{G. Robustness of the \mden{} Differences} 
	\label{app:robust}

    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
    robustness of the results using a few extra tests that are illustrated in
    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
    are briefly described here:

        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
            Given the small sample size, we extend slightly toward lower \mtot{} range 
            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
            Although the smaller sample leads to larger statistical uncertainties, 
            we can still see similar structural differences in both \mtot{} bins, 
            and the difference becomes more significant in the higher \mtot{} bin.  
            For the lower \mtot{} bin, the difference in the inner region becomes 
            quite uncertain, while the difference in the outskirt is still visible. 
            This potentially suggests that the environmental dependence of structure 
            also varies with \mstar{}, an important implication deserves more 
            investigations in the future.

        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
            Despite the larger uncertainties due to smaller samples, we find the 
            results are the same.

        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
            in overlapped \mhalo{} distributions with the \nbcg{} samples 
            considering the typical uncertainty of $\lambda$.
            This makes the difference in the inner region slightly less significant, 
            but the overall results are the same.

        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
            profiles to the largest radius allowed.  
            The \mmax{} values are less reliable than \mtot{} due to the 
            uncertainty of background subtraction and contamination from nearby 
            bright objects, but they can serve as different estimates of the ``total''
            \mstar{} of these galaxies.
            As shown in Section~\ref{sec:discussion}, they on average increase
            the \mstar{} by a little bit and affect the \rbcg{} more.
            The differences in the \mden{} profiles still remain very similar.

    We also test the robustness of the \mtot{}-matched results using the samples with 
    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
    samples without the ones in very massive halos ($\lambda > 40$).  
    Limited by space, we do not show these results here, but they all verify the 
    robustness of the results.

    For the results from the \minn{}-matched samples:

        \item
            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
            at the same time.  
            This makes the two median \mden{} profiles very similar inside 10-15 
            kpc, while the result in the outskirt remains the same (left panel of 
            Fig~\ref{fig:prof_4}).
            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.

        \item 
            To make sure the two samples are comparable in their overall assembly history,
            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
            in both samples. 
            This excludes the \nbcg{} galaxies that are much less massive and 
            more ``compact'' in structure. 
            Yet, the results regarding the structural differences remain the same.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
      \caption{
          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
          and higher (right; [11.7, 11.9]) \mtot{} bins. 
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          The difference in median profiles is more significant in higher \mtot{} bin.
          }
      \label{fig:prof_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_3}
      \caption{
        Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
        The formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
        The differences are, here, the samples are matched in slightly differnt ways. 
        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
        c) using \mstar{} within 150 kpc instead of 100 kpc.
        The results are broadly consistent with the one in Fig~\ref{fig:prof_1}.
        }
      \label{fig:prof_3} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
      \caption{
          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
          inner region. 
          Left panel shows the results after matching the \minn{} and \meff{} together, 
          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
          \rbcg{} and \nbcg{} galaxies are included.
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          }
      \label{fig:prof_4} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
\section{A. Extraction of 1-D surface brightness profile} 
    \label{app:ellipse}

@@

    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
    objects around the target.
    At the depth of the HSC images, this becomes a challenging task, especially 
    for massive galaxies with extended outer profiles and many satellites. 
    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
    we therefore perform \texttt{SExtractor}-like background subtraction and object 
    detection using the \texttt{SEP} Python library to generate the necessary masks.
    Combining two different local background models and $S/N$ thresholds, we obtain 
    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
    the one that is close to the center of bright galaxy (left panel of 
    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
    information. 
    We first create the mask that covers all contaminating objects around the target 
    after adaptively increasing the sizes of their masks according to their brightness 
    and distance to the target center. 
    Generally speaking, we mask out the very bright objects or objects in the 
    outskirt of the target a little more aggressively as they could impact the 
    low surface brightness regions more significantly. 
    We also create masks that are less and more aggressive to test their impacts
    on the surface brightness profiles.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
    \label{app:sed}

@@
